---
title: "420-hw2"
author: "Ting Wang"
output: html_document
date: "2023-10-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(MASS)
library(mvtnorm)
```

# Problem 1 - a
```{r}
sigma_R1 <- 0.03
sigma_R2 <- 0.02
cov <- function(rho) {
  matrix(c(sigma_R1^2, rho*sigma_R1*sigma_R2, rho*sigma_R1*sigma_R2, sigma_R2^2), ncol = 2)
}

corr <- function(rho) {
  matrix(c(1,rho,rho,1), ncol = 2)
}
cov
corr
```

# Problem 1-b
```{r}
# Expectation of the portfolio
E_Rtotal <- 0+0
E_Rtotal
```

```{r}
rhos <- seq(-1,1,by=0.01)
vars <- sigma_R1^2 + sigma_R2^2 + 2*rhos*sigma_R1*sigma_R2
vola <- sqrt(vars)
plot(rhos, vola, type = 'l',xlab = "correlation - rho", ylab = "volatility - sigma", main = "The volatility sigma as a function of correlation - rho")
```


# Problem 1-c
Based on the plot we have, I think it is better to have a lower correlation between $R_1$ and $R_2$, because we can use the volatility will be lower if the correlation is lower in the plot, such as the volatility is less than 0.005 when corrlation is -1. 


In the follwing, set $\rho$ = 0.5
# Problem 1-d
```{r}
rho <- 0.5
var_R <- function(rho) {
  return(sigma_R1^2 + sigma_R2^2 + 2*rho*sigma_R1*sigma_R2)
}

sigma <- sqrt(var_R(0.5))
sigma

mu <- E_Rtotal
mu
```

# problem 1-f
The distribution of $L^{total}$ is the same as the distribution of R.
```{r}
mu_L <- -mu
sigma_L <- -sigma
var_L <- (-sigma)^2
mu_L
sigma_L
var_L
```

# Problem 1-g
```{r}
mu_return <- c(0,0)
rho <- 0.5
cov_R <- cov(0.5)
# suppose we calculate 1000 days
return_R <- mvrnorm(1000, mu = mu_return, Sigma = cov_R)

loss_L <- -return_R

portfolio_L <- 500*loss_L[,1] + 1000*loss_L[,2]
var <- quantile(portfolio_L,0.01)
var
```


# Problem 1-h
```{r}
mu_R <- c(0,0)
sigma_R <- c(0.03,0.02)
rho <- 0.5
P <- pmvnorm(lower = c(-Inf, -Inf), upper=c(-1,-1), mean = mu_R, sigma = cov(0.5))
union <- pnorm(-1,mu_R[1],sigma_R[1]) + pnorm(-1,mu_R[2]+sigma_R[2]) - P
union
```
I do not think this is a serious concern in the example, because the probability is not very high, around 15.386%. In this way, we could know that the return below -1 is not happen often. 

# Problem 3-b

# Problem 3-b
```{r}
pnorm(0.25) - pnorm(-0.4167)
```


```{r}
pt(0.1941, df=5) - pt(-0.3416, df=5) 

```


